%% start of file `my-resume.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv} 
\moderncvstyle{casual}
\moderncvcolor{blue}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

\usepackage[utf8]{inputenc}

% ajustes para los margenes de pagina
\usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{3cm}

% personal data
\name{Vedat}{Kilic}
\title{Expert Full Stack Developer}
\phone[mobile]{+90~(532)~569~02~22}
\email{kilicvedat@gmail.com}
\social[linkedin]{vedatkilic}
\social[twitter]{vedtkilic}
\social[github]{vedatkilic}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------

\makecvtitle

\section{Experience}
\cventry{2021--Ongoing}{Software Engineering Consultant}{\href{https://web.derayah.com/}{Derayah}}{Riyadh}{Saudi Arabia}{
\begin{itemize}%
  \item A team member that works on the core components of the system which includes: customer creation, accounts operations and transactions processing.
  \item Implementing core banking functionalities, analysing business requirements, writing technical documentation, solving production issues
  \item ava 11, Spring Boot, Elasticsearch, Kibana, Apache Avro, Kafka, Confluent, Maven, Git, Docker, Kubernetes \end{itemize}
}
\cventry{2021--Ongoing}{Managing Partner}{\href{http://nivorbit.com}{Nivorbit}}{Canakkale}{Turkey}{
\begin{itemize}
  \item Microservice Technologies 
  \item DevOps Processes
  \item Service Development
  \item Architectural Management
\end{itemize}  
}
\cventry{2020--Ongoing}{Software Engineering Consultant}{\href{https://www.n11.com}{N11}}{Istanbul}{Turkey}{
\begin{itemize}%
  \item Development, Designing, Maintenance of an e-commerce platform
  \item Responsible for 50+ Microservices
  \item Supporting teams how to manage, design, develop and deploy microservices based on Spring Boot, Go, Node, Java and Kotlin
  \item Supporting devops how to design pipelines and deploy microservices based on Kubernetes(OpenShift), Jenkins, Tekton with CRDs \end{itemize}
}
\cventry{2020--2020}{Expert Software Developer}{\href{https://www.ozan.com}{Ozan}}{Istanbul}{Turkey}{
\begin{itemize}%
  \item Development, Designing of a digital money platform based on multiple tenant
  \item Cloud native backend and front-end architecture
  \item Management and Leading of multinational development team based on London, Malta, Sophia, Istanbul
  \item Designing CD/CI Pipelines based on Jenkins, Tekton, Kubernetes (Google Cloud) \end{itemize}
}
\cventry{2020--2020}{Expert Software Developer}{\href{https://www.ozan.com}{Ozan}}{Istanbul}{Turkey}{
\begin{itemize}%
  \item Development, Designing of a digital money platform based on multiple tenant
  \item Cloud native backend and front-end architecture
  \item Management and Leading of multinational development team based on London, Malta, Sophia, Istanbul
  \item Designing CD/CI Pipelines based on Jenkins, Tekton, Kubernetes (Google Cloud) \end{itemize}
}
\cventry{2019--2020}{Expert Full Stack Developer}{\href{https://www.turkcell.com.tr}{Turkcell}}{Istanbul}{Turkey}{
\begin{itemize}%
  \item A member of {\href{https://business.fizy.com/}{fizy-business}} team (https://business.fizy.com), Online Music Streaming Platform for Business.
  \item Development, Designing of a stream music application for business
  \item Designing fast, scalable, cloud native backend and front-end architecture
  \item Development of web player for browsers, MacOSX, Windows, Linux and Raspberry Pi
  \item Remote updating of web player and remote connection to web player
  \item Designed, architected and implemented microservices with Spring Cloud Netflix Microservice Architecture, Spring Boot 2.x, Java 1.8 Functional \end{itemize}
}
\cventry{2019--2019}{Senior Full Stack Developer}{\href{https://www.openpayd.com}{OpenPayd}}{London}{United Kingdom}{
\begin{itemize}%
  \item Development, Maintenance of FinTech products, exclusively for London-based start-ups and corporations of larger scale.
  \item Lead and mentored the team
  \item Designing, architecting and writing event driven microservices using Axon Framework, Spring Cloud Stream, RabbitMQ, Kafka with a constraint to handle transactions of 10,000/sec.
  \item Development, Maintenance of front-end app based on Angular 7
  \item Refactored the application from monoliths to micro services with Spring Boot, Java, Docker, Kubernetes and custom scripts.
  \item Designing API-driven banking and payments technology.
  \item Creation of new customer experiences by embedding financial services.
  \item Building new functionality fast, with modular, API-powered tech.
  \item Building a banking and payments service that grows and change, simple, developer-first API delivers Banking-as-a-Service with a modular architecture. \end{itemize}
}
\cventry{2017--2019}{Senior Full Stack Developer - Scrum Master}{Turkcell Technology Research and Development}{Istanbul}{Turkey}{
\begin{itemize}%
  \item A member of {\href{http://fizy.com}{fizy}} team (http://fizy.com), Online Music Streaming Platform.
  \item Worked with a team of 20 people, developers, QA and scrum masters, working as scrum master
  \item Lead the team
  \item Designed, architected and wrote the front-end of music application using Angular with 1,000 reusable components
  \item Modernized front-end app originally built on JQuery to Angular
  \item Optimized service layers, request queues and data model to handle request load of 74,000-96,000/sec during rush hours
  \item Built CI/CD pipelines using Jenkins, Docker and custom scripts - helping teams deploy without downtime
  \item Designed, architected and wrote microservices with Spring Cloud Netflix Microservice Architecture, Spring Boot 2.x, Java 1.8 Functional and replatform project from monoliths to microservices.
  \item Improved application performance to handle 1,000+ concurrent requests and also be multi-threaded.
  \item Log management with ELK, and advanced text search with Solr\&Elastic Search \end{itemize}
}
\cventry{2013--2017}{Senior Software Specialist}{Garanti Technology}{Istanbul}{Turkey}{
\begin{itemize}%
  \item Worked on development of cross-platform highly scalable seamless mobile banking infrastructure based on hybrid architecture.
  \item Made high-level design choices, dictated technical standards including software coding standards, tools and platforms.
  \item Lead and mentored the team.
  \item Solved technical, security and performance issues of web sites and applications for all tiers in infrastructure.
  \item Made performance and stress tests collaborating with system, network and other related groups.
  \item Designed and developed architecture of integrating social media with digital banking channels.
  \item Worked on personal and corporate Internet banking development using Java, Maven, Spring, JavaScript, jQuery, Objective-C.
  \item Provided solutions for general problems and enhancements. \end{itemize}
}
\cventry{2013}{R\&D Engineer}{Kentkart}{Izmir}{Turkey}{\begin{itemize}%
  \item Designed hardware for GPS Tracking, Electronic Payment System and Transportation System.
  \item Advanced PL/SQL, Performance Tuning of Queries, Oracle Database, Database Design and Query Optimization.
  \item Application development with technologies: PHP, Java, JSP, Javascript, JQuery, CSS, HTML5, SOAP, REST, .NET.
\end{itemize}}
\cventry{2011}{Internship}{Dokuz Eylul University}{Izmir}{Turkey}{\begin{itemize}%
  \item Power card design for electronic circuit.
  \item Electronic card design with Altera, Proteus and Pspice.
\end{itemize}}
\cventry{2011}{Internship}{ASELSAN}{Ankara}{Turkey}{ASELSAN is a Turkish corporation that produces tactical military radios and defense electronic systems for the Turkish Armed Forces.\begin{itemize}%
  \item Designed laser marking hardware of tank shot system.
  \item Developed software about laser marking of tank shot system using programming languages and technologies: FPGA, C, C++, Qt.
\end{itemize}}
\cventry{2010}{Internship}{Turkish Radio and Television Corporation (TRT)}{Istanbul}{Turkey}{\begin{itemize}%
  \item Designed Network, Maintained Network and Performance Tuning of Network.
\end{itemize}}

\section{Skills}
\cvitem{Team \& Agile Collaboration}{Collaboration, communication, planning \& estimation, agile development practices, Scrum}
\cvitem{Back-End Development}{API design and development, app architecture, micro-services, Node.js, PHP, C\#.NET, Java, Kotlin, JUnit, Spring, Spring Boot, Spring Cloud, Maven, Gradle, REST, SOAP}
\cvitem{Front-End Development}{JavaScript (ES5, ES6), React, AngularJs, Polymer, HTML5, CSS3, Sass}
\cvitem{Mobile}{Swift, Objective-C, Java, RxJava}
\cvitem{Others}{C, C++, Java, Kotlin, PL/SQL, SQL, OpenCV, OpenGL, Git, SVN, CA SCM}
\cvitem{Database}{Database architecture, modeling, query optimization, MySQL, PostgreSQL, MongoDB, Oracle}
\cvitem{Developer Operations}{Google Cloud, OpenShift, AWS, Heroku, Kubernetes, Docker, Kafka, RabbitMQ, Consul, Github, Bitbucket, Tomcat, JBoss, Websphere, Visual Studio Code, PL/SQL Developer, Eclipse, IntelljIDE, XCode, Interface Builder, Android Studio, Atom, SublimeText, Microsoft SQL Server}
  
\section{Education}
\cventry{2010--2013}{BS, Computer Engineering}{Dokuz Eylul University}{Turkey}{}{Ranked 3rd in Computer Engineering Department in terms of CGPA (3.5/4).}
\cventry{2007--2013}{BS, Electrical and Electronics Engineering}{Dokuz Eylul University}{Turkey}{}{Ranked 1st in E\&E Engineering Department in terms of CGPA (3.62/4).}

\section{Projects}
\cventry{}{Iwa}{Website \& Mobile Application}{\href{http://www.iwaport.com/customer/home}{Web}}{\href{https://play.google.com/store/apps/details?id=com.iwasoft.iwa}{Android} - \href{https://apps.apple.com/de/app/iwa/id1352023984}{IOS}}{A insurance and billing tracking system, mobile application for Android and IOS, website.}
\cventry{}{CoachWiz}{Mobile Application}{\href{https://play.google.com/store/apps/details?id=com.optimistlifecoach.tr}{Android}}{}{Access all the information you need for your coaching on the go anytime, anywhere.}
\cventry{}{Vehicle Tracking System}{Website \& Mobile Application \& Hardware Design}{}{}{A vehicle tracking system based on BeagleBone. Includes cross-browser website, mobile application for Android and IOS and desktop application for all operating system based on Qt.}
\cventry{}{IDE for 8051 Intel Microprocessor}{Qt Application}{}{}{Developed an IDE for 8051 microprocessor. IDE includes a 8051 simulator, memory map, lexical and syntax analyzer and I/O pin voltage level led indicator.}
\cventry{}{Android Mobile Phone Tracking System by using GPS, Wi-Fi, Cell-ID}{Android Application}{}{}{Tracking system for phone which has Android OS and show current position of phone on map online.}
\cventry{}{Design and Implementation of an Unnamed Flying Object: Quadrotor}{}{}{}{Designed a quadrotor with four propellers. Implemented and designed hardware of quadrotor, developed open source quadrotor software based on Kalman Filter and PID Space Equation.}
\cventry{}{Design and Realization of an Automation System using Microcontroller Based IO Units and Ethernet Network}{}{}{}{Designed an alternative system to PLC using PIC microprocessor.}
\cventry{}{Symbolic Circuit Analyzer}{}{}{}{Designed simple and user-friendly electronic circuit analyzer like Pspice. Program includes state equation of circuit according to I/O selection.}
\cventry{}{Android Employee Login-Logout System with RFID Card Reader}{Android Application}{}{}{Phone based employee entry-exit tracking system for companies.}

\end{document}

%% end of file `my-resume.tex'.
